---
title: "7. Termin"
author: "Lena Heidrich"
date: "2024-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r }
library(palmerpenguins)
names(penguins)
fit <-lm(body_mass_g ~ species + sex, data = penguins)
summary(fit)
fit2 <- glm(sex~ species + body_mass_g, family = binomial, data = penguins)
bill_ratio <- penguins$bill_depth_mm/(penguins$bill_length_mm + penguins$bill_depth_mm)
hist(bill_ratio)
fit3 <- glm(bill_ratio ~ sex + species, data = penguins, family = quasibinomial)
summary(fit3)

```

Datensatz earnings

```{r }
library(foreign)
setwd("~/SE R WiSe 24")
earns <- read.dta("heights.dta")
names(earns)

fit4 <- lm(earn ~ height, data = earns)
summary(fit4)

```
Größe hat Einfluss auf Gehalt

Muss kontrollieren für Geschlecht => Unterschied für Geschlecht
```{r }
fit5 <- lm(earn ~ height + sex, data = earns)
summary(fit5)
```





Aufgabe: neues Markdown erstellen

```{r }
knitr::opts_chunk$set(echo = TRUE)

library(foreign)
library(ggplot2)

#load data
setwd("~/SE R WiSe 24")
earns <- read.dta("heights.dta")
names(earns)
```

##Earnings depend on height
A little known fact is that earnings depend on height.

```{r }
fit5 <- summary(lm(earn ~ height + sex, data = earns))
```
As we can see it is a small effect relative to sex.

## Interaction with sex

What we do not yet known,

This can be visualized in a plot of earnings on height

```{r }
ggplot(earns, aes(x = height, y = earn, color = sex)) +
  geom_point() +
  geom_smooth(method = "lm", aes(group = sex)) +
  theme_classic()
```